SubGenome Analysis

### 2017-08-04 R/SubGenome Analysis.Rmd
Minor

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
```
```{r preamble, echo=FALSE}
paste("This analysis is using the file", params$inputDataFile)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyr)
library(ggplot2)
```
```{r preamble, echo=FALSE}
paste("This analysis is using the file", params$inputDataFile)
```
